Regional and Urban Economics

### 2023-02-19 Retail Agglomeration_Theory.qmd
Manlende referanser

The Bertrand model was introduced as early as in 1883 and demonstrate two firms competing by simultaneously setting prices for their homogeneous products.
Furthermore, the consumers choose the product with the lowest price.
The model assumes that firms have identical production cost and consumers have perfect information about prices.

By combining elements from the two models a hybrid model of spatial completion was birthed by Salop in 1979.
In this model firms compete both in location and price, with consumers having a transportation cost and firms producing differentiated products.

@@

Marshall also points out the competition within the geographical location.
Hence, the marketplace and business districts give consumers low search and switching costs @capello2015.
The fact that owners of stores seem to prefer highly concentrated shopping.
More-so, it suggests that the sales volumes outweigh the loss attributed to greater price competition@capello2015.

>>>>

The Bertrand model was introduced as early as in 1883 and demonstrate two firms competing by simultaneously setting prices for their homogeneous products.
Furthermore, the consumers choose the product with the lowest price@tolotti2020. The model assumes that firms have identical production cost and consumers have perfect information about prices @tolotti2020.

By combining elements from the two models a hybrid model of spatial completion was birthed by Salop in 1979 @tolotti2020. In this model firms compete both in location and price, with consumers having a transportation cost and firms producing differentiated products @tolotti2020.

@@

Marshall also points out the competition within the geographical location.
Hence, the marketplace and business districts give consumers low search and switching costs @capello2015.
The fact that owners of stores seem to prefer highly concentrated shopping.
More-so, it suggests that the sales volumes outweigh the loss attributed to greater price competition\@capello2015.
